\phantomsection
\addcontentsline{toc}{chapter}{Further Reading}

\begin{thebibliography}{}

\subsection*{OpenGeoSys Literature}

\bibitem{kalbacher:modelling}
Kalbacher T, Mettier R, et al.: Geometric modelling and object-oriented software concepts applied to a heterogeneous fractured network from the grimsel rock laboratory.
\emph{Comput Geosci,} \textbf{11(1):} 9--26 (2007)

\bibitem{kolditz:clean}
Kolditz O, Bauer S, Bilke L, et al.: OpenGeoSys: An open source initiative for numerical simulation of thermo-hydro-mechanical/chemical (THM/C) processes in porous media. \emph{Environ Earth Sci,} \textbf{67(2):}589--599 (2012)

\bibitem{kolditz:book}
Kolditz O, Görke J-U, Shao H, Wang W (Eds): Thermo-Hydro-Mechanical-Chemical Processes in Fractured Media. Springer Berlin-Heidelberg, ISBN:978-3-642-27176-2, (2012)

\bibitem{ogs:web}
OpenGeoSys -- scientific software for coupled processes in porous media,
\texttt{http://www.opengeosys.org}

\bibitem{ogs:wiki}
OpenGeoSys-Wiki: Source code, current projects, presentations and much more. \texttt{https://svn.ufz.de/ogs/}

\bibitem{wang:thm}
Wang W, Kolditz O: Object-oriented finite element analysis of thermo-hydro-mechanical (THM) problems in porous media.
\emph{Int J Numer Meth Engng,} \textbf{69:}162--201 (2007)

\bibitem{wang:pfem}
Wang W, Kosakowski G, Kolditz O: A parallel finite element scheme for thermo-hydro-mechanical (THM) coupled problems in porous media \emph{Comput Geosci,} \textbf{35(8):}1631--1641 (2009)


\subsection*{Data Explorer Literature}

\bibitem{rink:envirvis}
Rink K, Bilke L, Kolditz O: Visualisation Strategies for Modelling and Simulation Using Geoscientific Data. \emph{Proc. of Workshop on Visualisation of Environmental Data, Leipzig Germany,} p. 47--51, The EuroGraphics Association.

\bibitem{rink:iemss}
Rink K, Bilke L, Selle B, Kolditz O: User Guided Generation of Hydrological Models: Interface Design, Workflows and Concepts for an Extensible Software Framework. \emph{Proc. of 6th
Int Congress on Environmental Modelling and Software (iEMSs2012), Leipzig, Germany,} (2012)

\bibitem{rink:modelcare}
Rink K, Fischer T, Gräbe A, Kolditz O: Visual Preparation of Hydrological Models. In \emph{Models -- Repositories of Knowledge,} IAHS Redbook \#355, ISBN: 978-1-907161-34-6, 113--118, (2012)

\bibitem{rink:cgvcvip}
Rink K, Fischer T, Kolditz O: Data Visualisation and Validation for Hydrological Models. \emph{Proc. of International Conference on Computer Graphics, Visualization, Computer Vision and Image Processing (CGVCVIP2011), Rome, Italy,} p. 169--176, (2011)

\bibitem{rink:catchres}
Rink K, Fischer T, Selle B, Kolditz O: A Data Exploration Framework for Validation and Setup of Hydrological Models.
\emph{Environ Earth Sci,} \textbf{69(2):}469--477, (2013)

\bibitem{rink:iwas}
Rink K, Kalbacher T, Kolditz O: Visual Data Exploration for Hydrological Analysis. \emph{Environ Earth Sci,} \textbf{65(5):} 1395--1403 (2012)


\subsection*{Case Studies}

\bibitem{gräbe:deadsea}
Gräbe A, Rödiger T, Rink K, et al.: Numerical analysis of the groundwater regime in the western Dead Sea escarpment, Israel + West Bank. \emph{Environ Earth Sci,} \textbf{69(2):}571--585, (2013)

\bibitem{selle:wess}
Selle B, Rink K, Kolditz O: Recharge and discharge controls on groundwater travel times and flow paths to production wells for the Ammer catchment in SW Germany. \emph{Environ Earth Sci,} \textbf{69(2):}443--452, (2013)

\bibitem{sun:nankou}
Sun F, Shao H, Wang W, et al.: Groundwater deterioration in Nankou--a suburban area of Beijing: data assessment and remediation scenarios. \emph{Environ Earth Sci,} \textbf{67(6):}1573--1586, (2012)


\subsection*{Cited Literature}

\bibitem{knupp:quality}
P. M. Knupp: Achieving finite element mesh quality via optimization of the Jacobian matrix norm and associated quantities. Part I--a framework for surface mesh optimization. \emph{Int J Numer Meth Eng,} \textbf{48:}401--420, (2000)

\bibitem{shewchuk:quality}
J. R. Shewchuk: What is a Good Linear Finite Element? Interpolation, Conditioning, Anisotropy, and Quality Measures. \emph{Department of Electrical Engineering and Computer Science, University of Berkeley,} (2002)

\bibitem{tetgen:software}
H. Si: TetGen -- A Quality Tetrahedral Mesh Generator and Three-Dimensional Delaunay Triangulator. \emph{WIAS Technical Report No. 13,} Weierstrass Institute for Applied Analysis and Stochastics, (2013) \\
\url{http://www.tetgen.org}

\bibitem{geuzaine:gmsh}
C. Geuzaine and J.-F. Remacle: Gmsh: a three-dimensional finite element mesh generator with built-in pre- and post-processing facilities. \emph{Int J Numer Meth Eng,} \textbf{79(11):}1309--1331, (2009) \\
\url{http://geuz.org/gmsh}

\end{thebibliography} 